Column {data-width=300}
-------------------------------------

<font style="font-size: 25px">Parameters </font> 
    
###
    
Separate probabilities by comma.
```{r}
textInput("etaJ_binary", "Probability of observing components", value = "0.9,0.5", width = NULL,
          placeholder = NULL)
```


Parameters of Beta prior:
```{r}
fluidRow(
    column(width = 6, numericInput('alpha', 'alpha', 1, step = .1, min = 0)),
    column(width = 6, numericInput('beta', 'beta', 1, step = .1, min = 0))
)
```

Test:
    ```{r}
fluidRow(
    column(width = 6, numericInput('minp_binary', 'Null hypothesis', .1, step = .1, min = 0, max = 1)),
    column(width = 6, numericInput('size_binary', 'Size of test', .05, step = .01, min = 0, max = 1))
)
```



```{r}
actionButton('run_binary', 'Run')
```





Column {data-width=350}
-------------------------------------
    
<font style="font-size: 25px">The optimal PAP</font>     
    
```{r}
#object to store calculation results
v_binary = reactiveValues()

observeEvent(input$run_binary, {
    v_binary$etaJ = unlist(strsplit(input$etaJ_binary, ",")) |> as.numeric()
    
    # Check if input values are valid numerical vector
    v_binary$valid_inputs = check_inputs_binary_data(etaJ = v_binary$etaJ,
                                                     minp = input$minp_binary, size = input$size_binary,
                                                     a = input$alpha, b = input$beta)
    
    if (v_binary$valid_inputs){ 
        # The optimal test
        v_binary$output_optimal = pap_binary_data(etaJ = v_binary$etaJ,
                                                  minp = input$minp_binary, size = input$size_binary,
                                                  a = input$alpha, b = input$beta) 
        v_binary$output_optimal$test = v_binary$output_optimal$test |>
            filter(t>0) |>
            arrange(t)
        
        # The simple test
        v_binary$output_simple = pap_binary_data_simple(etaJ = v_binary$etaJ,
                                                        minp = input$minp_binary, size = input$size_binary,
                                                        a = input$alpha, b = input$beta)
        
    } else {
        v_binary$output_optimal$test = "Invalid input values"
        v_binary$output_optimal$expected_power = NaN
        v_binary$output_simple$test = NaN
        v_binary$output_simple$expected_power = NaN
    }
})
```


### Expected power {data-height=150}

```{r}
renderValueBox({
  valueBox(round(mean(v_binary$output_optimal$expected_power), digits=2))
})
```

### {data-height=750}
```{r}
renderTable({
    req(v_binary$output_optimal)
    v_binary$output_optimal$test
},
digits = 2
)
```




### {data-height=75}

```{r}
downloadLink("download_binary", "Download the optimal PAP (csv file)", style = "font-size: 20px;")
output$download_binary = 
    downloadHandler(
    filename = paste(Sys.Date(), "_binary_pap.csv", sep = ""),
    content = function(file) {
        write_csv(v_binary$output_optimal$test, file)
    }
)
```

Column {data-width=350}
-------------------------------------

<font style="font-size: 25px">The optimal simple PAP</font> 

### Expected power {data-height=150}

```{r}
renderValueBox({
  valueBox(round(mean(v_binary$output_simple$expected_power), digits=2))
})
```

### {data-height=400}
```{r}
renderTable({
    req(v_binary$output_simple)
    v_binary$output_simple$test
},
digits = 2
)
```



### Notes {data-height=450}

For optimal PAPs, each row of the table shows a possible combination of values for X, and the corresponding rejection probability t of the optimal full data test.
Values of X that are not displayed have t = 0 (no rejection).

For simple cutoff rules, the table shows the components of X used by the test, the cutoff in terms of the sum of these components, and the rejection probability when the sum is exactly at the cutoff.
