Column {data-width=300}
-------------------------------------

<font style="font-size: 25px">Parameters</font> 

###

Separate entries by comma.
```{r}
textInput("etaJ_normal", "Probability of observing components", value = "0.9,0.5", width = NULL,
  placeholder = NULL)
```


Parameters of Normal prior:
```{r}
fluidRow(
    column(width = 5, textInput("mu", "Prior mean vector", value = "1,1", width = NULL,
                                placeholder = NULL)),
    column(width = 7, textInput("Sigma", "Prior variance matrix", value = "2,1,1,2", width = NULL,
                                placeholder = NULL))
)
```

Test:
```{r}
fluidRow(
    column(width = 5, textInput("mu0", "Null mean vector", value = "0,0", width = NULL,
                                placeholder = NULL)),
    column(width = 7, textInput("Sigma0", "Null variance matrix", value = "1,0,0,1", width = NULL,
              placeholder = NULL))
)

numericInput('size_normal', 'Size of test', .05, step = .01, min = 0, max = 1)
```


```{r}
actionButton('run_normal', 'Run')
```



Column {data-width=350}
-------------------------------------

<font style="font-size: 25px">The optimal PAP</font> 

```{r}
#object to store calculation results
v_normal = reactiveValues()

observeEvent(input$run_normal, {
    v_normal$etaJ = unlist(strsplit(input$etaJ_normal, ",")) |> as.numeric()
    v_normal$mu0 = unlist(strsplit(input$mu0, ",")) |> as.numeric()
    v_normal$n = length(v_normal$mu0)
    v_normal$Sigma0 = unlist(strsplit(input$Sigma0, ",")) |> as.numeric() |> 
        matrix(nrow = v_normal$n)
    v_normal$mu = unlist(strsplit(input$mu, ",")) |> as.numeric()
    v_normal$Sigma = unlist(strsplit(input$Sigma, ",")) |> as.numeric() |> 
        matrix(nrow = v_normal$n)
    v_normal$plot_test = F # Flag for plotting 2d optimal testing rule
    
    # Check if input values are valid numerical vector
    v_normal$valid_inputs = check_inputs_normal_data(etaJ = v_normal$etaJ, 
                                                     mu0 = v_normal$mu0, Sigma0 = v_normal$Sigma0,
                                                     mu = v_normal$mu, Sigma = v_normal$Sigma,
                                                     size = input$size_normal)
    
    if (v_normal$valid_inputs){  
        # The optimal test
        v_normal$output_optimal = pap_normal_data(etaJ = v_normal$etaJ, 
                                                  mu0 = v_normal$mu0, Sigma0 = v_normal$Sigma0,
                                                  mu = v_normal$mu, Sigma = v_normal$Sigma,
                                                  size = input$size_normal)
        v_normal$output_optimal$test_display = 
            v_normal$output_optimal$test |>
            filter(t>0) |> 
            select(paste0("X", 1:v_normal$n), "t")
        v_normal$plot_test = (v_normal$n == 2) 
        
        # The simple test
        v_normal$output_simple = pap_normal_data_simple(etaJ = v_normal$etaJ, 
                                                        mu0 = v_normal$mu0, Sigma0 = v_normal$Sigma0,
                                                        mu = v_normal$mu, Sigma = v_normal$Sigma,
                                                        size = input$size_normal)
        v_normal$output_simple$test_display = v_normal$output_simple$test
        
        
    } else {
        v_normal$output_optimal$test = "Invalid input values"
        v_normal$output_optimal$expected_power = NaN
        v_normal$output_simple$test = NaN
        v_normal$output_simple$expected_power = NaN
    }
})
```

### Expected power {data-height=75}

```{r}
renderValueBox({
  valueBox(round(mean(v_normal$output_optimal$expected_power), digits=2))
})
```

### {data-height=400}
```{r}
renderTable({
    req(v_normal$output_optimal)
    v_normal$output_optimal$test_display
  },
  digits = 2
)
```

### Plot for the 2d case
```{r}
bound = 4
renderPlot({
    req(v_normal$output_optimal)
    if (v_normal$plot_test){ 
        v_normal$output_optimal$test |> 
            plot_2d_normal()
    }
  }
)

```


### {data-height=75}

```{r}
downloadLink("download_normal", "Download the optimal PAP (csv file)", style = "font-size: 20px;")
output$download_normal = 
    downloadHandler(
    filename = paste(Sys.Date(), "_normal_pap.csv", sep = ""),
    content = function(file) {
      write_csv(v_normal$output_optimal$test, file)
    }
  )
```

Column {data-width=350}
-------------------------------------

<font style="font-size: 25px">The optimal simple PAP</font> 

### Expected power {data-height=75}

```{r}
renderValueBox({
  valueBox(round(mean(v_normal$output_simple$expected_power), digits=2))
})
```

### {data-height=400}
```{r}
renderTable({
    req(v_normal$output_simple)
    v_normal$output_simple$test_display
  },
  digits = 2
)
```


### Notes

For optimal PAPs, each row of this table shows a possible combination of upper and lower values for X, and the corresponding rejection probability t of the optimal full data test.
Values of X that are not displayed have t = 0 (no rejection).

For simple cutoff rules, the table shows the components of X used by the test, and the cutoff in terms of the sum of these components.



